The problem and promise of scale in animal social multilayer networks

### 2020-02-09 paper/manuscript.Rmd
m-m-m-more refzzzzz

Social processes, movement decisions, and space use are inextricably linked 
and multilayer networks represent a potential analytical framework for linking 
these processes [@Mourier_2019]. Movement as a collective group can 
reduce per capita predation risk via detection-dilution trade-offs and improve 
information transfer about the quality or location of resources to other group 
members [@Jolles_2019]. In our case study, we integrate proximity based 
social networks that inherently rely on animal collective movement and, in general, 
we found that movement is likely an important mechanism driving social network 
connectivity within and between habitat types.

Although multilayer animal social networks are relatively novel [@Silk_2018], 
movement behaviour within multilayer networks has been considered.  Spatial
networks are physical locations (nodes) which are connected in a network when individuals
move between said locations (edges). For example, spatial networks were applied
to monitor movement of sharks (*Carcharhinus amblyrhynchos* and *Carcharhinus
melanopterus*) between fixed location autonomous arrays. In this example, nodes
represent locations within the array, *intralayer edges* represent individual
movement frequency, and *interlayer edges* represent contact probability among
individuals at a given node [@Mourier_2019]. Although movement between 
fixed arrays is inherent, networks are not constructed based on continuous 
measures of dyadic or collective movement [@Long_2014]. Our case study 
builds on the work of Mourier et al. (2019) and explicitly integrates 
continuous and simultaneous measures of animal movement through space 
and time as layers of a multilayer social network.

In contrast to spatial networks, where nodes represent spatial locations that
are fixed in space, movement networks can represent continuous and simultaneous
movement trajectories of multiple animals. In a recent study of vulturine 
gunieafowl (Acryllium vulturinum), GPS movement data were used to generate 
monolayer association networks within a multilayer network [@Papageorgiou_2019]. 
However, despite potential to generate networks in different spatial or social contexts, 
layers in the multilayer network represented social associations within and 
between groups. Continuous collection of animal relocation data using GPS 
technology can be used to measure how groups of animals make collective 
movement decisions in the context of their local environment (Strandburg-Peshkin et al. 2015, 2017) and across scales. A
collective movement layer could constitute similarity in movement for dyads
[@Long_2014] or groups  [@Bode_2011]. This movement layer could be
made at a fine [i.e. minute-to-minute: @Cleasby_2019] or coarse scale
[global migration: @Flack_2018]. Our case study integrates variation 
in temporal and spatial scale to assess the role of scale in predicting 
multilayer networks. As one might expect, we found increasing spatial 
scale results in saturation of potential social connections (Figure 3), 
while increasing temporal scale had little effect on habitat-specific 
networks (Figure 5). Another potential application would be to
generate social networks during times when animals are engaged in different
behaviours, including traveling, interacting, or foraging [@Muller_2018; @Finn_2019] 
and construct a multilayer network based on behaviour-specific monolayer 
networks [e.g. @Smith_Aguilar_2019].

Importantly, the key to incorporating movement in multilayer networks across
scales is the technological advancements available to overcome previous
limitations [@Hughey_2018]. Biologging and wildlife tracking technology 
has advanced to the point where relocations can be programmed to occur as 
frequently as each second [@Börger_2016], a practice which has been applied 
to questions of collective movement (e.g Strandburg-Peskin et al. 2015). 
Meanwhile, remote sensing technology, including unmanned aerial vehicles 
and satellites, can be used to track the fine-scale movements of groups 
over large distances and time scales (Torney et al. 2019). Using 
technology to infer behaviour has therefore become standard operating procedure
for many species in many systems. Our ability to collect and process 
remotely sensed data and infer social processes based on animal movement 
provides an opportunity to use multilayer social network analysis to answer
complex questions about animal socioecology.

Given the existing framework for constructing multilayer networks from
behavioural layers [e.g. @Smith_Aguilar_2019], monolayer networks that
explicity quantify movement paramters could be itnegrated. For example, edges 
could represent measures of dyadic or collective movement based on dynamic 
interaction metrics [@Long_2014]. Integrating movement layers
with habitat-specific social association layers could further shed light on the
role of movement as a driver of the social and spatial environments an
individual experiences [@Webber_2018]. In our case study, we
generated multilayer networks based on habitat-specific monolayers. Coordinated
movement of dyads, or groups, could vary based on habitat, and the approach we
outline could be used to explore mechanisms linking the social and spatial
environments. For example, social processes may be an emergent property of the
landscape because animals aggregate at resources, such as waterholes
(Chamaillé-Jammes et al. 2008). Movement to, from, or within habitat patches  or
territories can also contribute to the formation of the social environment
(Spiegel et al. 2016). For example, in sleepy lizards (*Tiliqua rugosa*) males
interacted primarily at home range edges, presumably driving territorial
behaviour (Spiegel et al. 2018). Incorporating movement ecology within a
multilayer network framework is a logical next step for a burgeoning field. In
particular, when association networks are habitat-specific, we suggest the
integration of movement and space use in multilayer networks provides novel
insights into the effects of habitat configuration on the formation of the
social environment [@He_2019].

>>>>

Social processes, movement decisions, and space use are inextricably linked 
and multilayer networks represent a potential analytical framework for linking 
these processes [@Mourier_2019] (Mourier et al. 2019). Movement as a collective group can 
reduce per capita predation risk via detection-dilution trade-offs and improve 
information transfer about the quality or location of resources to other group 
members [@Jolles_2019]. In our case study, we integrate proximity based 
social networks that inherently rely on animal collective movement and, in general, 
we found that movement is likely an important mechanism driving social network 
connectivity within and between habitat types.

Although multilayer animal social networks are relatively novel [@Silk_2018], 
movement behaviour within multilayer networks has been considered.  Spatial
networks are physical locations (nodes) which are connected in a network when individuals
move between said locations (edges). For example, spatial networks were applied
to monitor movement of sharks (*Carcharhinus amblyrhynchos* and *Carcharhinus
melanopterus*) between fixed location autonomous arrays. In this example, nodes
represent locations within the array, *intralayer edges* represent individual
movement frequency, and *interlayer edges* represent contact probability among
individuals at a given node [@Mourier_2019] (Mourier et al. 2019). Although movement between 
fixed arrays is inherent, networks are not constructed based on continuous 
measures of dyadic or collective movement [@Long_2014]. Our case study 
builds on the work of Mourier et al. (2019) and explicitly integrates 
continuous and simultaneous measures of animal movement through space 
and time as layers of a multilayer social network.

In contrast to spatial networks, where nodes represent spatial locations that
are fixed in space, movement networks can represent continuous and simultaneous
movement trajectories of multiple animals. In a recent study of vulturine 
gunieafowl (*Acryllium vulturinum*), GPS movement data were used to generate 
monolayer association networks within a multilayer network [@Papageorgiou_2019]. 
However, despite potential to generate networks in different spatial or social contexts, 
layers in the multilayer network represented social associations within and 
between groups. Continuous collection of animal relocation data using GPS 
technology can be used to measure how groups of animals make collective 
movement decisions in the context of their local environment 
[@Strandburg_Peshkin_2015; @Strandburg_Peshkin_2017] and across scales. A
collective movement layer could constitute similarity in movement for dyads
[@Long_2014] or groups  [@Bode_2011]. This movement layer could be
made at a fine [i.e. minute-to-minute: @Cleasby_2019] or coarse scale
[global migration: @Flack_2018]. Our case study integrates variation 
in temporal and spatial scale to assess the role of scale in predicting 
multilayer networks. As one might expect, we found increasing spatial 
scale results in saturation of potential social connections (Figure 3), 
while increasing temporal scale had little effect on habitat-specific 
networks (Figure 5). Another potential application would be to
generate social networks during times when animals are engaged in different
behaviours, including traveling, interacting, or foraging [@Muller_2018; @Finn_2019] 
and construct a multilayer network based on behaviour-specific monolayer 
networks [e.g. @Smith_Aguilar_2019].

Importantly, the key to incorporating movement in multilayer networks across
scales is the technological advancements available to overcome previous
limitations [@Hughey_2018]. Biologging and wildlife tracking technology 
has advanced to the point where relocations can be programmed to occur as 
frequently as each second [@Börger_2016], a practice which has been applied 
to questions of collective movement [e.g @Strandburg_Peshkin_2015]. 
Meanwhile, remote sensing technology, including unmanned aerial vehicles 
and satellites, can be used to track the fine-scale movements of groups 
over large distances and time scales [@Torney_2018]. Using 
technology to infer behaviour has therefore become standard operating procedure
for many species in many systems. Our ability to collect and process 
remotely sensed data and infer social processes based on animal movement 
provides an opportunity to use multilayer social network analysis to answer
complex questions about animal socioecology.

Given the existing framework for constructing multilayer networks from
behavioural layers [e.g. @Smith_Aguilar_2019], monolayer networks that
explicity quantify movement paramters could be itnegrated. For example, edges 
could represent measures of dyadic or collective movement based on dynamic 
interaction metrics [@Long_2014]. Integrating movement layers
with habitat-specific social association layers could further shed light on the
role of movement as a driver of the social and spatial environments an
individual experiences [@Webber_2018]. In our case study, we
generated multilayer networks based on habitat-specific monolayers. Coordinated
movement of dyads, or groups, could vary based on habitat, and the approach we
outline could be used to explore mechanisms linking the social and spatial
environments. For example, social processes may be an emergent property of the
landscape because animals aggregate at resources, such as waterholes
[@Chamaillé_Jammes_2008]. Movement to, from, or within habitat patches  or
territories can also contribute to the formation of the social environment
(Spiegel et al. 2016). For example, in sleepy lizards (*Tiliqua rugosa*) males
interacted primarily at home range edges, presumably driving territorial
behaviour (Spiegel et al. 2018). Incorporating movement ecology within a
multilayer network framework is a logical next step for a burgeoning field. In
particular, when association networks are habitat-specific, we suggest the
integration of movement and space use in multilayer networks provides novel
insights into the effects of habitat configuration on the formation of the
social environment [@He_2019].
